# (PART\*) Appetizers {-}

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
library(gt)
library(readr)
library(icons)
library(fontawesome)
library(purrr)
library(stringr)
library(tidyr)
library(dplyr)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Functions, variables, and data
pepper_on <- fontawesome::fa("pepper-hot", fill = "#A62014", height = "2em")
pepper_off <- fontawesome::fa("pepper-hot", fill = "#9FC2B9", height = "2em")

spicy0 <- paste0(pepper_off, pepper_off, pepper_off)
spicy1 <- paste0(pepper_on, pepper_off, pepper_off)
spicy2 <- paste0(pepper_on, pepper_on, pepper_off)
spicy3 <- paste0(pepper_on, pepper_on, pepper_on)

colour1 <- "#153331"
colour2 <- "#1E6E6E"

# Description function
description_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(icon = dplyr::case_when(
      difficulty == 0 ~ purrr::map(spicy0, gt::html),
      difficulty == 1 ~ purrr::map(spicy1, gt::html),
      difficulty == 2 ~ purrr::map(spicy2, gt::html),
      difficulty == 3 ~ purrr::map(spicy3, gt::html)
    )) %>%
    dplyr::select(description, icon) %>%
    gt::gt() %>%
    gt::cols_width(description ~ gt::px(500),
                   icon ~ gt::px(200)) %>%
    gt::cols_align(align = "left",
                   columns = description) %>%
    gt::cols_align(align = "right",
                   columns = icon) %>%
    gt::cols_label(description = gt::md("**Description**"),
                   icon = gt::md("")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour1)
}

ingredients_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(packages = stringr::str_replace_all(packages, " ", "<br>")) %>%
    dplyr::select(packages, data) %>%
    gt::gt() %>%
    gt::tab_header(title = "Ingredients") %>%
    gt::cols_width(packages ~ gt::px(350),
                   data ~ gt::px(350)) %>%
    gt::cols_align(align = "center",
                   columns = c(packages, data)) %>%
    gt::cols_label(packages = gt::md("**Package**"),
                   data = gt::md("**Data**")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour2) %>%
    gt::fmt_markdown(columns = tidyr::everything())
}

# Source data used to create the data recipes
recipe_data <- readr::read_csv("/home/ryangarnett/Github/recipe_book/data/source_recipes.csv")
```

# Accessing Packages
R is a power programming language for data and statistical analysis. The language has many excellent functionalities that allow for various data and statistical analysis. R can be extended by adding features outside the base functionality, which is done by adding packages. A package is a collection of functionality made available within a single installation. R has a great community with many individuals and organizations who develop and publish packages free of charge. Within this section will explore how to install and load packages within the RStudio environment.

## Installing Packages
Packages can be installed within RStudio in either a code block or within the console section of RStudio.

### Install a Single Package
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(1)
ingredients_table(1)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
install.packages("package_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
install.packages("readr")
```


### Install Multiple Packages
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(2)
ingredients_table(2)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
install.packages(c("package_name1","package_name2", "package_name3"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
install.packages(c("readr", "dplyr", "tidyr"))
```

## Loading Pagages
Once a package has been installed into RStudio it must be loaded into the RStudio environment. Each time you write code (i.e. a RNotebook, RMarkdown document, script, etc.) the specific packages that will be used must be loaded. The most common method for loading packages is to place the commands within a code block section.

### Load a Single Package
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(3)
ingredients_table(3)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
library(package_name)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
library(readr)
```

### Load Multiple Packages
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(78)
ingredients_table(78)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
library(package_name1)
library(package_name2)
library(package_name3)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
library(readr)
library(dplyr)
library(tidyr)
```
