```{r echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
library(gt)
library(readr)
library(icons)
library(fontawesome)
library(purrr)
library(stringr)
library(tidyr)
library(dplyr)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Functions, variables, and data
pepper_on <- fontawesome::fa("pepper-hot", fill = "#A62014", height = "2em")
pepper_off <- fontawesome::fa("pepper-hot", fill = "#9FC2B9", height = "2em")

spicy0 <- paste0(pepper_off, pepper_off, pepper_off)
spicy1 <- paste0(pepper_on, pepper_off, pepper_off)
spicy2 <- paste0(pepper_on, pepper_on, pepper_off)
spicy3 <- paste0(pepper_on, pepper_on, pepper_on)

colour1 <- "#153331"
colour2 <- "#1E6E6E"

# Description function
description_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(icon = dplyr::case_when(
      difficulty == 0 ~ purrr::map(spicy0, gt::html),
      difficulty == 1 ~ purrr::map(spicy1, gt::html),
      difficulty == 2 ~ purrr::map(spicy2, gt::html),
      difficulty == 3 ~ purrr::map(spicy3, gt::html)
    )) %>%
    dplyr::select(description, icon) %>%
    gt::gt() %>%
    gt::cols_width(description ~ gt::px(500),
                   icon ~ gt::px(200)) %>%
    gt::cols_align(align = "left",
                   columns = description) %>%
    gt::cols_align(align = "right",
                   columns = icon) %>%
    gt::cols_label(description = gt::md("**Description**"),
                   icon = gt::md("")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour1)
}

ingredients_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(packages = stringr::str_replace_all(packages, " ", "<br>")) %>%
    dplyr::select(packages, data) %>%
    gt::gt() %>%
    gt::tab_header(title = "Ingredients") %>%
    gt::cols_width(packages ~ gt::px(350),
                   data ~ gt::px(350)) %>%
    gt::cols_align(align = "center",
                   columns = c(packages, data)) %>%
    gt::cols_label(packages = gt::md("**Package**"),
                   data = gt::md("**Data**")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour2) %>%
    gt::fmt_markdown(columns = tidyr::everything())
}

# Source data used to create the data recipes
recipe_data <- readr::read_csv("/home/ryangarnett/Github/recipe_book/data/source_recipes.csv")
```

# Creating Objects
Within R objects are stored within memory, allowing the object to be quickly accessed for analysis, modelling, and visualization. A common use of objects is to store data, however objects can be used to store many things, such as results from an equation, output from an analysis, functions, and even plots. In order to commit something to an object the `<-` assignment operator must be used. The following basic math equation will create a data object called x `x <- 1 + 1`, where the same basic math equation without the assignment operator will not create a data object `1 + 1`

This section will focus on creating data objects with later sections showing how the assignment operator can be used to make different objects.


## Variables
A variable is the storage of a single object. Variables can be created from providing specific values, or as a result of combining multiple variables together through adding, subtracting, multiplying, dividing, or a function.


### Create a character variable
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(4)
ingredients_table(4)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
object_name <- "text"
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
character_variable <- "Halifax"
```


### Create a numeric variable
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(5)
ingredients_table(5)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
object_name <- number
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
number_variable <- 10
```

### Create a variable from an equation
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(6)
ingredients_table(6)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
object_name <- number + number
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
total_variable <- 10 + 10
```

### Create a variable from combining variables
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(7)
ingredients_table(7)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
first_number_variable <- 5
second_number_variable <- 10
```

</br>


**Sample Instructions**
```{r eval=FALSE, include=TRUE}
object_name <- variable1 + variable2
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
combined_variable <- first_number_variable + second_number_variable
```

### Create a variable from a function
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(8)
ingredients_table(8)
```

</br>


**Sample Instructions**
```{r eval=FALSE, include=TRUE}
object_name <- function()
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
current_date_variable <- Sys.Date()
```


## Vectors
A vector is a simple data structure that stores a sequence of values. A requirement of a vector object is that all objects be of the same data type (i.e. character, integer, numeric, or logical). While basic vectors are a very useful data structure that are helpful in various data analytics situations.


### Create a character vector
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(9)
ingredients_table(9)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
object_name <- c("text", "text", "text")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
character_vector <- c("one", "two", "three")
```


### Create a numeric vector
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(10)
ingredients_table(10)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
object_name <- c(number, number, number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
number_vector <- c(1, 2, 3)
```


## Dataframe
A vector is a simple data structure that stores a sequence of values. A requirement of a vector object is that all objects be of the same data type (i.e. character, integer, numeric, or logical). While basic vectors are a very useful data structure that are helpful in various data analytics situations.

### Create dataframe with multiple character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(11)
ingredients_table(11)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
dataframe_name <- data.frame(first_column_name = c("text", "text", "text", "text"), second_column_name = c("text", "text", "text", "text"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
atlantic_provinces <- data.frame(province = c("NL", "NS", "PE", "NB"), capital = c("St John's", "Halifax", "Charlottetown", "Saint John"))
```


### Create dataframe with multiple numeric columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(12)
ingredients_table(12)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
dataframe_name <- data.frame(first_column_name = c(number, number, number, number), second_column_name = c(number, number, number, number))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
weather_station_temperatures <- data.frame(station_id = c(100, 101, 102, 103), temperature = c(10, 15.1, 6.3, -4.3))
```


### Create dataframe with multiple character and numeric columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(13)
ingredients_table(13)
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
dataframe_name <- data.frame(first_column_name = c(number, number, number, number), second_column_name = c("text", "text", "text", "text"), third_column_name = c(number, number, number, number), forth_column_name = c(number, number, number, number))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
atlantic_capital_temperatures <- data.frame(station_id = c(100, 101, 102, 103), province = c("NL", "NS", "PE", "NB"), city = c("St John's", "Halifax", "Charlottetown", "Saint John"), temperature = c(10, 15.1, 6.3, -4.3))
```
