```{r echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
library(gt)
library(readr)
library(icons)
library(fontawesome)
library(purrr)
library(stringr)
library(tidyr)
library(dplyr)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Functions, variables, and data
pepper_on <- fontawesome::fa("pepper-hot", fill = "#A62014", height = "2em")
pepper_off <- fontawesome::fa("pepper-hot", fill = "#9FC2B9", height = "2em")

spicy0 <- paste0(pepper_off, pepper_off, pepper_off)
spicy1 <- paste0(pepper_on, pepper_off, pepper_off)
spicy2 <- paste0(pepper_on, pepper_on, pepper_off)
spicy3 <- paste0(pepper_on, pepper_on, pepper_on)

colour1 <- "#153331"
colour2 <- "#1E6E6E"

# Description function
description_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(icon = dplyr::case_when(
      difficulty == 0 ~ purrr::map(spicy0, gt::html),
      difficulty == 1 ~ purrr::map(spicy1, gt::html),
      difficulty == 2 ~ purrr::map(spicy2, gt::html),
      difficulty == 3 ~ purrr::map(spicy3, gt::html)
    )) %>%
    dplyr::select(description, icon) %>%
    gt::gt() %>%
    gt::cols_width(description ~ gt::px(500),
                   icon ~ gt::px(200)) %>%
    gt::cols_align(align = "left",
                   columns = description) %>%
    gt::cols_align(align = "right",
                   columns = icon) %>%
    gt::cols_label(description = gt::md("**Description**"),
                   icon = gt::md("")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour1)
}

ingredients_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(packages = stringr::str_replace_all(packages, " ", "<br>"),
                  data = stringr::str_replace_all(data, " ", "<br>")) %>%
    dplyr::select(packages, data) %>%
    gt::gt() %>%
    gt::tab_header(title = "Ingredients") %>%
    gt::cols_width(packages ~ gt::px(350),
                   data ~ gt::px(350)) %>%
    gt::cols_align(align = "center",
                   columns = c(packages, data)) %>%
    gt::cols_label(packages = gt::md("**Package**"),
                   data = gt::md("**Data**")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour2) %>%
    gt::fmt_markdown(columns = tidyr::everything())
}

# Source data used to create the data recipes
recipe_data <- readr::read_csv("~/Github/r-recipe-book/data/source_recipes.csv")
```

# Preview Data
Reviewing data is an important part of data analysis. There are many different methods to review data within R, however a common practice to review data is to manually visualize the values in columns of a dataframe. This section will explore options for manually exploring data within a dataframe.


## Inspect Data Structure
Prior to performing data analysis it is good to understand the elements, data types, and examples of the data within a dataframe. 


### Preview the structure of a dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(14)
ingredients_table(14)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
function(data)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
str(df)
```


## Preview Data
Manually reviewing data is a common practice to understand the data in a dataframe. R provides many options for manually reviewing dataframes.


### Subset of rows to preview in a dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(15)
ingredients_table(15)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
function(data)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
head(df)
```

### Specify a set number of rows to preview in a dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(16)
ingredients_table(16)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
function(data, number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
head(df, 100)
```

### Preview all rows of a dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(17)
ingredients_table(17)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
data
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
df
```

### Preview all rows of a dataframe within a viewer
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(17)
ingredients_table(17)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
function(data)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
View(df)
```
