# (PART\*) Breakfast {-}

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
library(gt)
library(readr)
library(icons)
library(fontawesome)
library(purrr)
library(stringr)
library(tidyr)
library(dplyr)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Functions, variables, and data
pepper_on <- fontawesome::fa("pepper-hot", fill = "#A62014", height = "2em")
pepper_off <- fontawesome::fa("pepper-hot", fill = "#9FC2B9", height = "2em")

spicy0 <- paste0(pepper_off, pepper_off, pepper_off)
spicy1 <- paste0(pepper_on, pepper_off, pepper_off)
spicy2 <- paste0(pepper_on, pepper_on, pepper_off)
spicy3 <- paste0(pepper_on, pepper_on, pepper_on)

colour1 <- "#153331"
colour2 <- "#1E6E6E"

# Description function
description_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(icon = dplyr::case_when(
      difficulty == 0 ~ purrr::map(spicy0, gt::html),
      difficulty == 1 ~ purrr::map(spicy1, gt::html),
      difficulty == 2 ~ purrr::map(spicy2, gt::html),
      difficulty == 3 ~ purrr::map(spicy3, gt::html)
    )) %>%
    dplyr::select(description, icon) %>%
    gt::gt() %>%
    gt::cols_width(description ~ gt::px(500),
                   icon ~ gt::px(200)) %>%
    gt::cols_align(align = "left",
                   columns = description) %>%
    gt::cols_align(align = "right",
                   columns = icon) %>%
    gt::cols_label(description = gt::md("**Description**"),
                   icon = gt::md("")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour1)
}

ingredients_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(packages = stringr::str_replace_all(packages, " ", "<br>")) %>%
    dplyr::select(packages, data) %>%
    gt::gt() %>%
    gt::tab_header(title = "Ingredients") %>%
    gt::cols_width(packages ~ gt::px(350),
                   data ~ gt::px(350)) %>%
    gt::cols_align(align = "center",
                   columns = c(packages, data)) %>%
    gt::cols_label(packages = gt::md("**Package**"),
                   data = gt::md("**Data**")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour2) %>%
    gt::fmt_markdown(columns = tidyr::everything())
}

# Source data used to create the data recipes
recipe_data <- readr::read_csv("/home/ryangarnett/Github/recipe_book/data/source_recipes.csv")
```

# Data Exploration
Data exploration is an essential part of data analytics, the preliminary step to data wrangling techniques, which will be covered in the next three chapters. Similar to other areas in R there are many different approaches to data exploration. This section will explore non data visualization data exploration techniques.

> *You can have data without information, but you cannot have information without data <br> Daniel Keys Moran*


## Selecting Data Columns
The size of data continues to grow, both in the number of rows and columns in a dataframe. Wide data, that with many columns, can provide challenges to data exploration, making it important to be able to limit and specify the columns that are used during data exploration.


### Select data by column name
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(33)
ingredients_table(33)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::select(df, column1)
```


### Select data by multiple column names
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(34)
ingredients_table(34)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name1, column_name2, column_name3, column_name4)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::select(df, column1, column2, column3, column4)
```


### Select data by column index
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(35)
ingredients_table(35)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::select(df, 1)
```


### Select data by multiple column index
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(36)
ingredients_table(36)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, number, number, number, number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::select(df, 1, 2, 5, 8)
```


### Select data by column index range
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(37)
ingredients_table(37)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, number:number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::select(df, 1:4)
```


### Select data by column index and column index range
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(38)
ingredients_table(38)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, number, number, number, number:number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::select(df, 1, 3, 5, 7:9)
```


### Select all but last column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(39)
ingredients_table(39)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, -1)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::select(df, -1)
```


## Filtering Data
Similar to reducing the number of columns during data exploration, it is important to be able to reduce the number of rows, which can be performed by creating a subsection of data based on a single, or multiple, values.


### Filter single column by character value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(40)
ingredients_table(40)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name == "text")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::select(df, country == "Canada")
```


### Filter single column by numeric value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(41)
ingredients_table(41)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name == number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, column1 == 5)
```


### Filter single column by multiple character values
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(42)
ingredients_table(42)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name %in% c("text", "text", "text"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, column1 %in% c("NS", "NB", "PE"))
```


### Filter single column by multiple numeric values
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(43)
ingredients_table(43)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name %in% c(number, number, number))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, column1 %in% c(5, 10, 15))
```


### Filter single column by range of numeric values
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(44)
ingredients_table(44)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, package::function(column, low value, high value))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, dplyr::between(column1, 5, 10))
```


### Filter numeric data larger than
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(45)
ingredients_table(45)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, > number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, column1 > 5)
```


### Filter numeric data smaller than
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(46)
ingredients_table(46)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, > number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, column1 < 5)
```


### Filter multiple columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(47)
ingredients_table(47)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column1 == "text", column2 == number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, column1 == "Canada", column2 == 10)
```


### Filter multiple columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(48)
ingredients_table(48)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column1 == "text" || column2 == number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, column1 == "Canada" || column2 == 10)
```


### Filter when multiple character values not in a column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(49)
ingredients_table(49)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, !column_name %in% c("text1", "text2", "text3"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::filter(df, !column1 %in% c("NS", "NB", "PE"))
```


## Combining Commands
### Select specific columns and filter column by character value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(50)
ingredients_table(50)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
data %>%
  package::function(column_name1, column_name2, column_name3) %>%
  package::function(column_name1 %in% c("text1", "text2", "text3"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
df %>%
  dplyr::select(column1, column2, column3) %>%
  dplyr::filter(column1 %in% c("NS", "NB", "PE"))
```
