```{r echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
library(gt)
library(readr)
library(icons)
library(fontawesome)
library(purrr)
library(stringr)
library(tidyr)
library(dplyr)
library(janitor)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Functions, variables, and data
pepper_on <- fontawesome::fa("pepper-hot", fill = "#A62014", height = "2em")
pepper_off <- fontawesome::fa("pepper-hot", fill = "#9FC2B9", height = "2em")

spicy0 <- paste0(pepper_off, pepper_off, pepper_off)
spicy1 <- paste0(pepper_on, pepper_off, pepper_off)
spicy2 <- paste0(pepper_on, pepper_on, pepper_off)
spicy3 <- paste0(pepper_on, pepper_on, pepper_on)

colour1 <- "#153331"
colour2 <- "#1E6E6E"

# Description function
description_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(icon = dplyr::case_when(
      difficulty == 0 ~ purrr::map(spicy0, gt::html),
      difficulty == 1 ~ purrr::map(spicy1, gt::html),
      difficulty == 2 ~ purrr::map(spicy2, gt::html),
      difficulty == 3 ~ purrr::map(spicy3, gt::html)
    )) %>%
    dplyr::select(description, icon) %>%
    gt::gt() %>%
    gt::cols_width(description ~ gt::px(500),
                   icon ~ gt::px(200)) %>%
    gt::cols_align(align = "left",
                   columns = description) %>%
    gt::cols_align(align = "right",
                   columns = icon) %>%
    gt::cols_label(description = gt::md("**Description**"),
                   icon = gt::md("")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour1)
}

ingredients_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(packages = stringr::str_replace_all(packages, " ", "<br>"),
                  data = stringr::str_replace_all(data, " ", "<br>")) %>%
    dplyr::select(packages, data) %>%
    gt::gt() %>%
    gt::tab_header(title = "Ingredients") %>%
    gt::cols_width(packages ~ gt::px(350),
                   data ~ gt::px(350)) %>%
    gt::cols_align(align = "center",
                   columns = c(packages, data)) %>%
    gt::cols_label(packages = gt::md("**Package**"),
                   data = gt::md("**Data**")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour2) %>%
    gt::fmt_markdown(columns = tidyr::everything())
}

# Source data used to create the data recipes
recipe_data <- readr::read_csv("/home/ryangarnett/Github/recipe_book/data/source_recipes.csv")
```

# Data Quality


> *Data quality requires a certain level of sophistication within a company to even understand that it's a problem <br> Colleen Graham <br>*


## Data Profiling

### Find duplicates in single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(55)
ingredients_table(55)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
janitor::get_dupes(df, country)
```


### Find duplicates in multiple columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(56)
ingredients_table(56)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name1, column_name2)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
janitor::get_dupes(df, country, capital)
```


## Data Cleaning


### Clean common header naming issues
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(51)
ingredients_table(51)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
janitor::clean_names(claims)
```


### Remove empty columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(52)
ingredients_table(52)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
janitor::remove_empty(claims)
```


### Remove empty rows
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(53)
ingredients_table(53)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
janitor::remove_empty_rows(claims)
```


### Remove empty rows and columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(54)
ingredients_table(54)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, which = c("rows", "cols")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
janitor::remove_empty(claims, which = c("rows", "cols")
```


### Convert null to specific character value in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(57)
ingredients_table(57)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, list(column_name = "text"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
tidyr::replace_na(df, list(country = "unknown"))
```


### Convert null to specific numeric value in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(58)
ingredients_table(58)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, list(column_name = number))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
tidyr::replace_na(df, list(population = -999))
```


### Remove leading whitespace from a character values in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(59)
ingredients_table(59)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name, side = c("right")))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, `Municipal Unit` = stringr::str_trim(`Municipal Unit`, side = c("right")))
```


### Remove trailing whitespace from a character values in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(60)
ingredients_table(60)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name, side = c("left")))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, `Municipal Unit` = stringr::str_trim(`Municipal Unit`, side = c("left")))
```


### Remove leading and trailing whitespace from a character values in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(61)
ingredients_table(61)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name, side = c("both")))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, `Municipal Unit` = stringr::str_trim(`Municipal Unit`, side = c("both")))
```


### Change all characters to lower case in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(62)
ingredients_table(62)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(x, `Civic Street Name` = stringr::str_to_lower(`Civic Street Name`))
```


### Change all characters to upper case in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(63)
ingredients_table(63)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(x, `Civic Street Name` = stringr::str_to_upper(`Civic Street Name`))
```


### Change all characters to title case in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(64)
ingredients_table(64)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(x, `Civic Street Name` = stringr::str_to_title(`Civic Street Name`))
```


### Change all characters to sentence case in a single column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(65)
ingredients_table(65)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(x, `Civic Street Name` = stringr::str_to_sentence(`Civic Street Name`))
```


### Remove punctuation from a single character column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(66)
ingredients_table(66)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name, "[[:punct:]]", ""))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, `Municipal Unit` = stringr::str_replace_all(`Municipal Unit`, "[[:punct:]]", ""))
```


### Change all spaces to underscores in a single character column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(67)
ingredients_table(67)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = package::function(column_name, " ", "_"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, `Municipal Unit` = str_replace_all(`Municipal Unit`, " ", "_"))
```


### Convert null with specific value in all character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(68)
ingredients_table(68)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, is.character, package::function, replace = "text")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate_if(df, is.character, tidyr::replace_na, replace = "unknown")
```


### Convert null with specific value in all numeric columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(69)
ingredients_table(69)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, is.numeric, package::function, replace = number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate_if(x, is.numeric, tidyr::replace_na, replace = -999)
```


### Remove whitespace in all character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(70)
ingredients_table(70)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, package::function(where(is.character), package::function))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, dplyr::across(where(is.character), stringr::str_trim))
```



### Change all characters to lower case in all character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(71)
ingredients_table(71)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, package::function(where(is.character), package::function))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(x, dplyr::across(where(is.character), stringr::str_to_lower))
```


### Change all characters to upper case in all character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(72)
ingredients_table(72)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, package::function(where(is.character), package::function))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(x, dplyr::across(where(is.character), stringr::str_to_upper))
```


### Change all characters to title case in all character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(73)
ingredients_table(73)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, package::function(where(is.character), package::function))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(x, dplyr::across(where(is.character), stringr::str_to_title))
```


### Change all characters to sentence case in all character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(74)
ingredients_table(74)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, package::function(where(is.character), package::function))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(x, dplyr::across(where(is.character), stringr::str_to_sentence))
```


### Remove punctuation from all character columns
```{r  eval=FALSE, include=TRUE}

```

```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(75)
ingredients_table(75)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, package::function(package::function(., "[[:punct:]]", "")))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate_all(df, dplyr::funs(stringr::str_replace_all(., "[[:punct:]]", "")))
```


### Change all spaces to underscores in all character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(76)
ingredients_table(76)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, package::function(package::function(., " ", "_")))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate_all(df, dplyr::funs(stringr::str_replace_all(., " ", "_")))
```


## Combining Commands
### Clean structure and values of a dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(77)
ingredients_table(77)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
data <- data %>%
  package::function() %>%
  package::function() %>%
  package::function(is.character, package::function, replace = "text") %>%
  package::function(is.numeric, package::function, replace = number) %>%
  package::function(package::function(where(is.character), package::function)) %>%
  package::function(package::function(where(is.character), package::function)) %>%
  package::function(package::function(package::function(., "[[:punct:]]", "")))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
data <- data %>%
  janitor::clean_names() %>%
  janitor::remove_empty() %>%
  dplyr::mutate_if(is.character, tidyr::replace_na, replace = "unknown") %>%
  dplyr::mutate_if(is.numeric, tidyr::replace_na, replace = -999) %>%
  dplyr::mutate(dplyr::across(where(is.character), stringr::str_trim)) %>%
  dplyr::mutate(dplyr::across(where(is.character), stringr::str_to_upper)) %>%
  dplyr::mutate_all(dplyr::funs(stringr::str_replace_all(., "[[:punct:]]", "")))
```






