```{r echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
library(gt)
library(readr)
library(icons)
library(fontawesome)
library(purrr)
library(stringr)
library(tidyr)
library(dplyr)
library(janitor)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Functions, variables, and data
pepper_on <- fontawesome::fa("pepper-hot", fill = "#A62014", height = "2em")
pepper_off <- fontawesome::fa("pepper-hot", fill = "#9FC2B9", height = "2em")

spicy0 <- paste0(pepper_off, pepper_off, pepper_off)
spicy1 <- paste0(pepper_on, pepper_off, pepper_off)
spicy2 <- paste0(pepper_on, pepper_on, pepper_off)
spicy3 <- paste0(pepper_on, pepper_on, pepper_on)

colour1 <- "#153331"
colour2 <- "#1E6E6E"

# Description function
description_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(icon = dplyr::case_when(
      difficulty == 0 ~ purrr::map(spicy0, gt::html),
      difficulty == 1 ~ purrr::map(spicy1, gt::html),
      difficulty == 2 ~ purrr::map(spicy2, gt::html),
      difficulty == 3 ~ purrr::map(spicy3, gt::html)
    )) %>%
    dplyr::select(description, icon) %>%
    gt::gt() %>%
    gt::cols_width(description ~ gt::px(500),
                   icon ~ gt::px(200)) %>%
    gt::cols_align(align = "left",
                   columns = description) %>%
    gt::cols_align(align = "right",
                   columns = icon) %>%
    gt::cols_label(description = gt::md("**Description**"),
                   icon = gt::md("")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour1)
}

ingredients_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(packages = stringr::str_replace_all(packages, " ", "<br>"),
                  data = stringr::str_replace_all(data, " ", "<br>")) %>%
    dplyr::select(packages, data) %>%
    gt::gt() %>%
    gt::tab_header(title = "Ingredients") %>%
    gt::cols_width(packages ~ gt::px(350),
                   data ~ gt::px(350)) %>%
    gt::cols_align(align = "center",
                   columns = c(packages, data)) %>%
    gt::cols_label(packages = gt::md("**Package**"),
                   data = gt::md("**Data**")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour2) %>%
    gt::fmt_markdown(columns = tidyr::everything())
}

# Source data used to create the data recipes
recipe_data <- readr::read_csv("~/Github/r-recipe-book/data/source_recipes.csv")
```

# Combining Data
It is very common to have data stored in multiple different tables or dataframes. For many data analysis approaches it is preferred to have multiple data sources in a single dataframe. This chapter will focus on combining multiple dataframes into a single dataframe.


## Appending Dataframes
Appending data is a common practice to combine multiple dataframes into a single dataframes without using common values between datasets to combine data.


### Add a dataframe to bottom of a dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(88)
ingredients_table(88)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample1.csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
rbind(data1, data2)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
rbind(df1, df2)
```


### Add a dataframe to right of a dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(89)
ingredients_table(89)
```

</br>

```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample1.csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
cbind(data1, data2)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
cbind(df1, df2)
```


## Joining Dataframes
Joining data is a common practice to combine multiple dataframes into a single dataframes based on common values within columns.


### Join with same joining column names
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(90)
ingredients_table(90)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, data2, by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::left_join(df1, df2, by = "user_id")
```


### Join with different joining names
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(91)
ingredients_table(91)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, data2, by = c("data1 column_name" = "data2 column_name"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::left_join(df1, df2, by = c("user_id" = "userid"))
```


### Join with subset of columns from one dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(92)
ingredients_table(92)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, package::function(data2, column_name1, column_name2, column_name3), by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::left_join(df1, dplyr::select(df2, user_id, product_purchased, purchase_amount), by = "user_id")
```


### Join with subset of columns from two dataframes
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(93)
ingredients_table(93)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(package::function(data1, column_name1, column_name2, column_name3), package::function(data2, column_name1, column_name2, column_name3), by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::left_join(dplyr::select(df1, user_id, first_name, last_name), dplyr::select(df2, user_id, product_purchased, purchase_amount), by = "user_id")
```


### Join matching rows in both dataframes
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(94)
ingredients_table(94)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, data2, by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::inner_join(df1, df2, by = "user_id")
```


### Join matching rows from the second dataframe to the first dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(95)
ingredients_table(95)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, data2, by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::left_join(df1, df2, by = "user_id")
```


### Join matching rows from the first dataframe to the first dataframe
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(96)
ingredients_table(96)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, data2, by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::right_join(df1, df2, by = "user_id")
```

### Join all rows regardless of matching
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(97)
ingredients_table(97)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, data2, by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::full_join(df1, df2, by = "user_id")
```


### Filter dataframe where matching rows between dataframes
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(98)
ingredients_table(98)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, data2, by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::semi_join(df1, df2, by = "user_id")
```


### Filter dataframe where non-matching rows between dataframes
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(99)
ingredients_table(99)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df1 <- readr::read_csv("C:/data/sample.1csv")
df2 <- readr::read_csv("C:/data/sample2.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data1, data2, by = "column_name")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::anti_join(df1, df2, by = "user_id")
```
