```{r echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
library(gt)
library(readr)
library(icons)
library(fontawesome)
library(purrr)
library(stringr)
library(tidyr)
library(dplyr)
library(janitor)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Functions, variables, and data
pepper_on <- fontawesome::fa("pepper-hot", fill = "#A62014", height = "2em")
pepper_off <- fontawesome::fa("pepper-hot", fill = "#9FC2B9", height = "2em")

spicy0 <- paste0(pepper_off, pepper_off, pepper_off)
spicy1 <- paste0(pepper_on, pepper_off, pepper_off)
spicy2 <- paste0(pepper_on, pepper_on, pepper_off)
spicy3 <- paste0(pepper_on, pepper_on, pepper_on)

colour1 <- "#153331"
colour2 <- "#1E6E6E"

# Description function
description_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(icon = dplyr::case_when(
      difficulty == 0 ~ purrr::map(spicy0, gt::html),
      difficulty == 1 ~ purrr::map(spicy1, gt::html),
      difficulty == 2 ~ purrr::map(spicy2, gt::html),
      difficulty == 3 ~ purrr::map(spicy3, gt::html)
    )) %>%
    dplyr::select(description, icon) %>%
    gt::gt() %>%
    gt::cols_width(description ~ gt::px(500),
                   icon ~ gt::px(200)) %>%
    gt::cols_align(align = "left",
                   columns = description) %>%
    gt::cols_align(align = "right",
                   columns = icon) %>%
    gt::cols_label(description = gt::md("**Description**"),
                   icon = gt::md("")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour1)
}

ingredients_table <- function(id){
  recipe_data %>%
    dplyr::filter(id == {{id}}) %>%
    dplyr::mutate(packages = stringr::str_replace_all(packages, " ", "<br>"),
                  data = stringr::str_replace_all(data, " ", "<br>")) %>%
    dplyr::select(packages, data) %>%
    gt::gt() %>%
    gt::tab_header(title = "Ingredients") %>%
    gt::cols_width(packages ~ gt::px(350),
                   data ~ gt::px(350)) %>%
    gt::cols_align(align = "center",
                   columns = c(packages, data)) %>%
    gt::cols_label(packages = gt::md("**Package**"),
                   data = gt::md("**Data**")) %>%
    gt::tab_options(heading.background.color = colour1,
                    column_labels.background.color = colour2) %>%
    gt::fmt_markdown(columns = tidyr::everything())
}

# Source data used to create the data recipes
recipe_data <- readr::read_csv("~/Github/r-recipe-book/data/source_recipes.csv")
```

# Modifying Data
When working with data it is common that values in columns need to be modified, or creating new columns of data. The following recipes outline how to change data with a column, and how to create data in a new column using different techniques.


## Static Value
Changing or creating data values in a column so that all rows have the same value; with examples for character, numeric, and date data types.

### Change or create a single character column with a static character value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(100)
ingredients_table(100)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = "text")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, country = "Canada")
```


### Change or create a single numeric column with a static numeric value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(101)
ingredients_table(101)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, population = 100000)
```


### Change a single date column with a static date value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(102)
ingredients_table(102)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name = "yyyy-mm-dd")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, date_added = "2021-11-19")
```


### Create a new date column with a static date value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(106)
ingredients_table(106)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = as.Date("yyyy-mm-dd"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, date_added = as.Date("2021-11-19"))
```


### Change or create multiple character columns with a static character value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(103)
ingredients_table(103)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name1 = "text",
                  column_name2 = "text")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, country = "Canada",
              country_code = "CA")
```


### Change or create multiple numeric columns with a static numeric value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(104)
ingredients_table(104)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name1 = number,
                  column_name2 = number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, population = 100000,
              growth_rate = 1.75)
```


### Change multiple date columns with a static date value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(105)
ingredients_table(105)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, column_name1 = "yyyy-mm-dd",
                  column_name2 = "yyyy-mm-dd")
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, date_added = "2021-11-19",
              date_changed = "2021-11-20")
```


### Create multiple new date columns with a static date value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(107)
ingredients_table(107)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name1 = as.Date("yyyy-mm-dd"),
                  new_column_name2 = as.Date("yyyy-mm-dd"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, date_added = as.Date("2021-11-19"),
              date_changed = as.Date("2021-11-20"))
```


## Using Existing Column(s)
Changing or creating data values in a column with values from an existing column of data; with examples for character, numeric, and date data types.

### Create new character column from static text and a character column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(108)
ingredients_table(108)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name, paste0("text", column_name))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, label = paste0("My name is ", first_name))
```


### Create new character column from multiple character columns
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(109)
ingredients_table(109)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name, paste0(column_name1, column_name2))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, username = paste0(first_name, last_name))
```


### Create new character column from multiple character columns and static text
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(110)
ingredients_table(110)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name, paste0(column_name1, " ", column_name2))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, legal_name = paste0(first_name, " ", last_name))
```


### Create new numeric column from a numeric column and a mathematical operation
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(111)
ingredients_table(111)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = column_name operator number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, cost_per_month = cost / 12)
```


### Create new numeric column from multiple numeric columns and mathematical operations
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(112)
ingredients_table(112)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = column_name1 operator column_name2)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, population_density = population / area_sq_km)
```


### Create new date column from a date column and a mathematical operation
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(114)
ingredients_table(114)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = column_name operator number)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, closing_date = date_created + 7)
```


### Create new date column from multiple date columns and mathematical operations
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(115)
ingredients_table(115)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = column_name1 operator column_name2)
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, duration = end_date - start_date)
```


### Create new date column from a date column and a function
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(116)
ingredients_table(116)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = package::function(column_name))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, year_created = lubridate::year(date_created))
```


## Conditionally from Existing Column
Creating data values in a new column using conditional statements from a existing column of data.


### Create new character column conditionally with default static value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(119)
ingredients_table(119)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = package::function(
  column_name operator number ~ "text",
  TRUE ~ "text"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, result = dplyr::case_when(
  score >= 50 ~ "pass",
  TRUE ~ "fail"))
```


### Create new character column conditionally with character column as default value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(120)
ingredients_table(120)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = package::function(
  column_name operator number ~ "text",
  TRUE ~ column_name))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(df, result = dplyr::case_when(
  grade == "F" ~ "Fail",
  TRUE ~ result))
```


### Create new character column conditionally from existing numeric column with default static value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(117)
ingredients_table(117)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = package::function(
  column_name operator number ~ "text",
  column_name operator number ~ "text",
  TRUE ~ "text"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(data, result = dplyr::case_when(
  score < 50 ~ "fail",
  score >= 50 ~ "pass",
  TRUE ~ "error"))
```


### Create new character column conditionally from range of values in existing numeric column with default static value
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(118)
ingredients_table(118)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = package::function(
  package::function(column_name, low_range, high_range) ~ "text",
  package::function(column_name, low_range, high_range) ~ "text",
  package::function(column_name, low_range, high_range) ~ "text",
  package::function(column_name, low_range, high_range) ~ "text",
  TRUE ~ "text"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(data, grade = dplyr::case_when(
  dplyr::between(score, 80, 100) ~ "A",
  dplyr::between(score, 70, 79) ~ "B",
  dplyr::between(score, 60, 69) ~ "C",
  dplyr::between(score, 50, 59) ~ "D",
  TRUE ~ "F"))
```


### Create new character column conditionally from specific values in a character column
```{r echo = FALSE, message = FALSE, warning = FALSE}
description_table(121)
ingredients_table(121)
```

</br>

**Preparation**
```{r eval=FALSE, include=TRUE}
df <- readr::read_csv("C:/data/sample.csv")
```

</br>

**Sample Instructions**
```{r eval=FALSE, include=TRUE}
package::function(data, new_column_name = package::function(
  column_name %in% c("text1", "text2", "text3", "text4") ~ "new value1",
  column_name == "text5" ~ "new value 2",
  column_name == "text6" ~ "new value 3",
  column_name %in% c("text7", "text8") ~ "new value4",
  column_name %in% c("text9", "text10") ~ "new value5",
  column_name %in% c("text11", "text12", "text13") ~ "new value6"))
```

</br>

**Actual Instructions**
```{r eval=FALSE, include=TRUE}
dplyr::mutate(data, region = dplyr::case_when(
  province_code %in% c("NL", "NS", "PE", "NB") ~ "Atlantic",
  province_code == "QC" ~ "Quebec",
  province_code == "ON" ~ "Ontario",
  province_code %in% c("MB", "SK") ~ "Praries",
  province_code %in% c("AB", "BC") ~ "Western",
  province_code %in% c("NU", "NT", "YK") ~ "Northern"))
```
